\newpage
\begin{thebibliography}{12}

\bibitem{tspbook}
D.L. Applegate, R.E. Bixby, V. Chvatal, and W.J. Cook. (2006). \textit{The Traveling Salesman Problem: A Computational Study}. Princeton: Princeton University Press. Retrieved: June 4, 2017.
Available: http://press.princeton.edu/chapters/s8451.pdf

\bibitem{Slides}
R.K.B. Bhattacharjya. (2013, November 7).
Introduction to Genetic Algorithms [Lecture slides from the Indian institute of Technology Guwahati]. Guwahati. Retrieved: May 12 2017. Available: https://www.iitg.ernet.in/rkbc/CE602/CE602/Genetic\%20Algorithms.pdf

\bibitem{Google}
Google.
\textit{Google Maps} [Google Maps distances].
Retrieved: May 19, 2017.

\bibitem{ORlecture}
 B. de Jonge. (2016). [Lecture slides from the University of Groningen]. Operations Research 1, Lecture 7: Network Theory 2. 

\bibitem{Congress}
L. Juan, C. Zixing, and L. Jianqin.
(2010). Premature convergence in genetic algorithm: Analysis and prevention based on chaos operator.
\textit{Proceedings of the 3rd World Congress on Intelligent Control and Automation}. 495-499.

\bibitem{Popdiv}
Y. Leung, Y. Gao, and Z. Xu. (1997).
Degree of Population Diversity - a Perspective on Premature Convergence in Genetic Algorithms and Its Markov Chain Analysis. \textit{IEEE Transactions on Neural Networks}, \textit{8}(5), 1165-1176. 

\bibitem{little}
J.D.C. Little, K.G. Murty, D.W. Sweeney and C. Karel. (1963). An algorithm for the traveling salesman problem. \textit{Operations Research}, \textit{11}(6), 972–989.

\bibitem{Basics}
M. Mitchell. (1998).
\textit{ An introduction to genetic algorithms.} Cambridge MA: MIT Press.

\bibitem{Premconvergence}
H.M. Pandey, A. Chadhary and D. Mehrota.
(2014). A Comparative Review of Approaches to Prevent Premature Convergence in GA. \textit{Applied Soft Computing}, \textit{24}, 1047-1077. 

\bibitem{populationsize}
B.R. Rajakumar and Aloysius George.(2013). APOGA: An Adaptive Population Pool Size Based Genetic Algorithm. \textit{AASRI Procedia}, \textit{4}, 288-96.

\bibitem{Thesis}
J.P. Ryan. (1992). 
\textit{An algorithm for the solution of a traveling salesman problem to minimize the average time to demand satisfaction} [Unpublished master's thesis]. Texas AM University. Retrieved: May 31, 2017.

\bibitem{Code}
O.H.P. Strik. (2017)
\textit{GAFramework} [The publication of the code]. 
Groningen. Available: https://github.com/Kranex/GAFramework

\end{thebibliography}


